results

### 2023-03-08 results_work.RMD
updated results

```{r packages}
library(tidyverse);library(readxl);library(lme4);library(emmeans);library(dplyr);library(cowplot);library(knitr);library(broom);library(rmarkdown);library(tinytex);library(tidyr);library(arsenal);library(magrittr);library(dabestr);library(nlme); library(pbkrtest);library(ggpubr); library(lmer)
```

@@

At baseline, there were no significant differences between training with glucose or placebo in muscle mass, isometric or isokinetic peak torque (Tab 1) or total session volume (Tab 2). Further, on pairwise consecutive days, there were no significant differences in mean macro nutrient (calories, carbohydrate, fat or protein) intake.

###### **Table 1:**  Baseline descriptives of legs allocated to RT with glucose or RT. LM = Lean mass, Strength = strength index, calculated from isometric and isokinetic peak torque, Iso 0 PT = Isometric (0 d/s) peak torque, Iso 60 PT = Isokinetic peak torque at 60 d/s, Iso 240 PT = Isokinetic peak torque at 240 d/s.
![](figures/desctab.png)
Glucose ingestion before and after RT led to significant increases in plasma levels of glucose and c-peptide before, during and after the session, compared to RT with placebo, (Fig 1B, 120min: 38 ± 4% [*p* = `r p.120`], 135min: 31 ± 4% [*p* = `r p.135`], 150min: 32 ± 4% [*p* = `r p.150`], Fig 1C, 120min: 95 ± 10% [*p* = `r cpp.120`], 150min: 87 ± 10% [*p* = `r cpp.150`]), measured during the sixth RT session. At 2hrs post-exercise, RT with glucose led to significantly lower plasma glucose levels compared to RT with placebo (1B, 270min: -8 ± 4% [*p* = `r p.270`].

######**Table 2:** Mean total session volume and mean change in total session volume from session 1 to session 6. 
![](figures/voltab.png)
There were no significant differences in change of skeletal muscle strength, at time points post 2 RT sessions, post 4 RT sessions, 30min after 6th session, 2hrs after 6th session and 23hrs after 6th session (Fig 1D, *p* > 0.05). After 5 RT sessions (Fig 1D, Post 5RT), there was a significant difference in strength between glucose and placebo,  where placebo decreased strength 7% more than glucose (*p* = `r pdiff.c4`).

@@

# For inline reporting
trcoef <- coef(summary(trna.lmod))
trdiff <- round(trcoef[3,1], 2)
trdiffp <- round(trcoef[3,5], 2)
trdiffse <- round(trcoef[3,2], 2)

@@

Resistance training with glucose did not induce a higher accumulation of total RNA (fig 2A, *p* = `r trdiffp`) or rRNA  (fig 2B, 47S: *p* = `r rr47diffp`, 18S: *p* = `r rr18diffp`, 28S: *p* = `r rr28diffp`, 5.8S: *p* = `r rr58diffp`, 5S: *p* = `r rr5diffp`) compared to RT with placebo, measured as mean change from baseline to post. From baseline to post-intervention, there was a mean increase in levels of total RNA by 26 and 22% after RT with glucose and placebo, respectively (*p* < 0.05, compared to baseline). A robust accumulation was also observed in ribosomal RNA expression in both RT with glucose and placebo, with mean increases between 34-43% (GLU) and 33-41% (PLAC) (*p* < 0.05, compared to baseline) in the four rRNA’s. The expression of the 47S pre-rRNA increased by 37 and 59% with glucose and placebo respectively, where only RT with placebo increased significantly from baseline to post (fig 45, *p* = `r rr47tdiffp`).

@@

ubf.rdy <- west.dat %>%  # One data frame without outliers
  select(subject, time, outlier, supplement, target, norm.sign) %>%
  filter(target == "ubf",
         outlier == "in") %>%
  select(-target) %>%
  group_by(subject, time, supplement) %>%
  summarise(mean.sign = mean(norm.sign, na.rm = TRUE)) %>%
  print()

rna.rdy <- rna.dat %>%
  select(subject, time, outlier, supplement, RNA.weight) %>%
  filter(outlier == "in") %>%
  mutate(subject = as.character(subject)) %>%
  group_by(subject, time, supplement) %>%
  summarise(mean.rna = mean(RNA.weight, na.rm = TRUE)) %>%
  print()

@@

  mutate(sd.ubf = (mean.sign - mean(mean.sign, na.rm = TRUE )/sd(mean.sign, na.rm = TRUE))) %>%
  print()

>>>>

```{r packages}
library(tidyverse);library(readxl);library(lme4);library(emmeans);library(dplyr);library(cowplot);library(knitr);library(broom);library(rmarkdown);library(tinytex);library(tidyr);library(arsenal);library(magrittr);library(dabestr);library(nlme); library(pbkrtest);library(ggpubr); library(nlme)
```

@@

At baseline, there were no significant differences between legs allocated to training with glucose or placebo in muscle mass, isometric or isokinetic peak torque (Tab 1). Total session volume (Tab 2) increased significantly from session 4 to session 6 compared to session 1 (*p* < 0.05), with no differences between exercising with glucose or placebo (*p* > 0.05). On pairwise consecutive days there were no significant differences in mean ingestion of protein, fat, carbohydrate or total calories (*p* > 0.05).

###### **Table 1:**  Baseline descriptives of legs allocated to RT with glucose or RT. LM = Lean mass, Strength = strength index, calculated from isometric and isokinetic peak torque, Iso 0 PT = Isometric (0 d/s) peak torque, Iso 60 PT = Isokinetic peak torque at 60 d/s, Iso 240 PT = Isokinetic peak torque at 240 d/s.
![](figures/tab1.png)
Glucose ingestion before and after RT led to significant increases in plasma levels of glucose (Fig 1B, 120min: 38 ± 4% [*p* = `r p.120`], 135min: 31 ± 4% [*p* = `r p.135`], 150min: 32 ± 4% [*p* = `r p.150`]) and c-peptide (Fig 1C, 120min: 95 ± 10% [*p* = `r cpp.120`], 150min: 87 ± 10% [*p* = `r cpp.150`]) before, during and after the session, compared to no change in placebo (*p* > 0.05). At 2hrs post-exercise, RT with glucose led to significantly lower plasma glucose levels compared to RT with placebo (1B, 270min: -8 ± 4% [*p* = `r p.270`].

######**Table 2:** Mean total session volume and mean change in total session volume from session 1 to session 6. 
![](figures/tab2.png)

After 5 RT sessions (Fig 1D, Post 5RT), there was a significant difference in strength between glucose and placebo,  where placebo decreased strength 7% more than glucose (Fig 1D, *p* = `r pdiff.c4`). At the remaining time points, there were no significant differences between exercising with glucose and placebo (*p* > 0.05). While both RT with glucose and placebo led to significantly reduced strength post fifth session compared to baseline (*p* < 0.05), there were no significant differences in strength at baseline and 23hrs post sixth RT session (Fig 1D, Baseline and 23h post 6RT).

@@

# For inline reporting
trcoef <- coef(summary(trna.lmod))
trdiff <- round(trcoef[3,1], 3)
trdiffp <- round(trcoef[3,5], 3)
trdiffse <- round(trcoef[3,2], 2)

@@

Resistance training with glucose did not induce a higher accumulation of total RNA (fig 2A, *p* = `r trdiffp`) or rRNA  (fig 2B, 47S: *p* = `r rr47diffp`, 18S: *p* = `r rr18diffp`, 28S: *p* = `r rr28diffp`, 5.8S: *p* = `r rr58diffp`, 5S: *p* = `r rr5diffp`) compared to RT with placebo. From baseline to post-intervention, there was a mean increase in levels of total RNA by 26 and 22% after RT with glucose and placebo, respectively (*p* < 0.05, compared to baseline). A robust accumulation was also observed in ribosomal RNA expression in both RT with glucose and placebo, with mean increases between 34-43% (GLU) and 33-41% (PLAC) (*p* < 0.05, compared to baseline) in the four rRNA’s. The expression of the 47S pre-rRNA increased by 37 and 59% with glucose and placebo respectively, where only RT with placebo increased significantly from baseline to post (fig 45, *p* = `r rr47tdiffp`).

@@

ubf.rdy <- west.dat %>%  # One data frame without outliers
  select(subject, time, outlier, supplement, target, norm.sign) %>%
  filter(target == "ubf",
         outlier == "in") %>%
  select(-target) %>%
  group_by(subject, time, supplement) %>%
  summarise(mean.sign = mean(norm.sign, na.rm = TRUE))

rna.rdy <- rna.dat %>%
  select(subject, time, outlier, supplement, RNA.weight) %>%
  filter(outlier == "in") %>%
  mutate(subject = as.character(subject)) %>%
  group_by(subject, time, supplement) %>%
  summarise(mean.rna = mean(RNA.weight, na.rm = TRUE))

@@

  mutate(sd.ubf = (mean.sign - mean(mean.sign, na.rm = TRUE )/sd(mean.sign, na.rm = TRUE)))
